---
title: "Age Cohort Comparisons"
author: "Deric Liang"
date: "6/24/2019"
output:
  pdf_document: default
  html_notebook: default
---


```{r results = "hide", include = FALSE}
library(tidyverse)
library(data.table)
library(survey)
library(mosaic)
```

```{r}
# read in main data
cididata_raw <-
  fread("ukrmain_RU_061419.csv")
```

# Data Cleaning

```{r}
# subsetting data
cididata_pt2 <-
  cididata_raw %>%
  # mental conditions
  mutate(anx = ifelse(DSM_AGO == 1|DSM_SO == 1|DSM_GAD == 1|DSM_PDS == 1, 1, 0),
         ied = ifelse(DSM_IEDH == 1, 1, 0),
         aff = ifelse(DSM_MDE == 1|DSM_DYS == 1, 1, 0),
         alc = ifelse(DSM_ALA == 1|DSM_ALD == 1, 1, 0),
         any = ifelse(anx == 1|ied == 1|aff == 1|alc == 1, 1, 0)) %>%
  # bromet age cohorts
  mutate(brom4_agecohort = cut(cididata_raw$AGE, breaks = c(16, 24, 34, 49, Inf),
                                        labels = c("Youngest", "Middle Young", "Middle Age", "Eldest")),
         brom3_agecohort = cut(cididata_raw$AGE, breaks = c(16, 37, 57, Inf),
                                      labels = c("Youngest", "Middle", "Eldest"))) %>%
  # alfonso age cohorts
  mutate(alfonso_cohort = cut(cididata_raw$AGE, breaks = c(16, 37, 49, 64, Inf),
                              labels = c("Youngest", "Middle Young", "Middle Age", "Eldest"))) %>%
  # select part 2 respondents
  filter(!is.na(de20)) %>%
  # religion
  mutate(de32_1 = as.factor(ifelse(is.na(de32_1), 0, 1)),
         de32_2 = as.factor(ifelse(is.na(de32_2), 0, 1)),
         de32_9 = as.factor(ifelse(is.na(de32_9), 0, 1)),
         de32_98 = ifelse(is.na(de32_98), 0, 1),
         de32_99 = ifelse(is.na(de32_99), 0, 1),
         de32_other = ifelse(de32_3 == 1|de32_4 == 1|de32_5 == 1|de32_6 == 1|de32_7 == 1|de32_8 == 1, 1, 0),
         de32_other = as.factor(ifelse(is.na(de32_other), 0, 1)),
         de34 = as.factor(ifelse(de34 == 8|de34 == 9, NA, de34))) %>%
  # suicidality
  mutate(ideate = ifelse(!is.na(sd2), sd2, sd15),
         plan = ifelse(!is.na(sd4), sd4, sd17),
         attempt = ifelse(!is.na(sd6), sd6, sd19),
         plan = ifelse(is.na(plan), 5, plan),
         attempt = ifelse(is.na(attempt), 5, attempt),
         ideate = as.factor(ifelse(ideate == 1, 1, 0)),
         plan = as.factor(ifelse(plan == 1, 1, 0)),
         attempt = as.factor(ifelse(attempt == 1, 1, 0))) %>%
  # married
  mutate(married = as.factor(ifelse(sc3 == 8|sc3 == 9, NA, 
                                    ifelse(sc3 == 1, 1, 0))),
         divorced = as.factor(ifelse(married == 0 & mr22 == 2|mr23 == 1, 1, 0)),
         single = as.factor(ifelse(married == 0 & mr16 == 5, 1, 0)),
         widowed = as.factor(ifelse(married == 0 & mr22 == 3|mr23 == 2, 1, 0)),
         marital_status = derivedFactor("married" = married == 1,
                                        "divorced" = divorced == 1,
                                        "widowed" = widowed == 1,
                                        "single" = single == 1,
                                        .method = "first")) %>%
  # chernobyl
  mutate(live_chernobyl = as.factor(ifelse(de40 == 1, 1, 
                                           ifelse(pt6a == 1 & !is.na(pt6a), 1,
                                                  ifelse(pt6b == 1 & !is.na(pt6b), 1, 0))))) %>%
  # social network
  mutate(SN1 = derivedVariable(`0` = sn1 == 6,
                               `1` = sn1 == 5,
                               `2` = sn1 == 4,
                               `3` = sn1 == 3,
                               `4` = sn1 == 2,
                               `5` = sn1 == 1,
                               `7` = sn1 == 7,
                               `8` = sn1 == 8,
                               `9` = sn1 == 9),
         SN2 = derivedVariable(`0` = sn2 == 6,
                               `1` = sn2 == 5,
                               `2` = sn2 == 4,
                               `3` = sn2 == 3,
                               `4` = sn2 == 2,
                               `5` = sn2 == 1,
                               `7` = sn2 == 7,
                               `8` = sn2 == 8,
                               `9` = sn2 == 9),
         SN6 = derivedVariable("1" = sn6 == 4,
                               "2" = sn6 == 3,
                               "3" = sn6 == 2,
                               "4" = sn6 == 1,
                               "2.5" = sn6 == 8|sn6 == 9),
         SN7 = derivedVariable("1" = sn7 == 4,
                               "2" = sn7 == 3,
                               "3" = sn7 == 2,
                               "4" = sn7 == 1,
                               "2.5" = sn7 == 8|sn7 == 9),
         SN1 = as.numeric(ifelse(SN1 == 7|SN1 == 8|SN1 == 9, NA, SN1)),
         SN2 = as.numeric(ifelse(SN2 == 7|SN2 == 8|SN2 == 9, NA, SN2)),
         SN6 = as.numeric(SN6),
         SN7 = as.numeric(SN7),
         sn_scale = (SN1 + SN2 -2)/8) %>%
  # financial status variable
  mutate(fnu4 = ifelse(fnu4 == 8|fnu4 == 9, NA, fnu4),
         financial_status = derivedFactor("very_inadequate" = fnu4 == 1,
                                          "inadequate" = fnu4 == 2|fnu4 == 3,
                                          "adequate" = fnu4 == 4|fnu4 == 5)) %>%
  # chronic conditions
  mutate(any_cc = as.factor(ifelse(cc1a == 1|cc1b == 1|cc1c == 1|cc1d == 1|cc1e == 1|
                           cc1f == 1|cc1g == 1|cc1h == 1|cc1i == 1|cc1j == 1|
                           cc1k == 1|cc1l == 1|cc1m == 1|cc1n == 1|cc1o == 1|
                           cc1p == 1|cc1q == 1|cc1r == 1|cc1s == 1|cc1t == 1|
                           cc1u == 1|cc1v == 1|cc1w == 1|cc1x == 1|cc1y == 1|
                           cc1tz == 1, 1, 0))) %>%
  # recode
  mutate(cc1tz = as.factor(ifelse(cc1tz == 8|cc1tz == 9, NA, 
                                  ifelse(cc1tz == 1, 1, 0))),
         cc2 = as.factor(ifelse(cc2 == 8|cc2 == 9, NA, cc2)),
         cn6 = as.factor(ifelse(cn6 == 8|cn6 == 9, NA,
                                ifelse(cn6 == 1, 1, 0))),
         cn6a = ifelse(cn6a == 98|cn6a == 99, NA, cn6a),
         ch67 = as.factor(ifelse(ch67 == 8|ch67 == 9, NA,
                                ifelse(ch67 == 1, 1, 0))),
         ch97 = as.factor(ifelse(ch97 == 8|ch97 == 9, NA,
                                ifelse(ch97 == 1, 1, 0))),
         ch52 = as.factor(ifelse(ch52 == 8|ch52 == 9, NA,
                                ifelse(ch52 == 1, 1, 0))),
         ch82 = as.factor(ifelse(ch82 == 8|ch82 == 9, NA,
                                ifelse(ch82 == 1, 1, 0))),
         fnu1 = ifelse(fnu1 == 8|fnu1 == 9, NA, fnu1),
         fnu4 = as.factor(ifelse(fnu4 == 8|fnu4 == 9, NA, fnu4)),
         pt1 = as.factor(ifelse(pt1 == 8|pt1 == 9, NA,
                                ifelse(pt1 == 1, 1, 0))),
         SEX = as.factor(SEX),
         emp = as.factor(emp),
         io16 = as.factor(io16)) %>%
  # select relevant variable
  select(sampleid, brom3_agecohort, alfonso_cohort, SEX, io16, 
         de20, fnu1, fnu4, financial_status, de32_1, de32_2, de32_other, de32_9, 
         emp, empw, empst, emph, empr, empoth, any_cc, de34, pt6a, pt6b, de40, 
         live_chernobyl, marital_status, sc3, mr16, mr22, mr23, sn_scale,
         sn1, sn2, sn6, sn7, SN1, SN2, SN6, SN7, cn6, cn6a, ideate, plan, attempt, ch67, 
         ch97, ch52, ch82, pt1, anx, alc, aff, ied, any, secu, strata, weight2)
```

```{r}
# Dataset with Part 2 weights on
SuicidePart2 <-
  svydesign(ids = ~secu, strata = ~strata, weights = ~weight2, nest = T, 
            data = subset(cididata_pt2, cididata_pt2$weight2>0))
options(survey.lonely.psu = "adjust")
```

# Frequency Tables

## Sex

```{r}
### 0 = female
### 1 = male
svytable(~alfonso_cohort + SEX, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + SEX, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```


## Marriage 

```{r}
# marital status
svytable(~brom3_agecohort + marital_status, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

## Chronic Conditions

```{r}
# presence of any chronic condition
svytable(~alfonso_cohort + any_cc, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + any_cc, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

## Socio-economic status

No tables for DE20 (years of schooling) or FNU1 (total monthly income); both are continuous variables and frequency tables inherently don't make sense for them.

```{r}
# financial status
svytable(~alfonso_cohort + financial_status, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + financial_status, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# employment status
### 1 = working
### 2 = student
### 3 = homemaker
### 4 = retired
### 5 = other

svytable(~alfonso_cohort + emp, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + emp, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

## Urbanicity

```{r}
### 1 = rural
### 2 = township
### 3 = city up to 200,000 inhabitants
### 4 = city between 200,000 and 500,000 inhabitants
### 5 = city with more than 500,000 inhabitants

svytable(~alfonso_cohort + io16, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort +io16, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

## Proximity to Chernobyl

```{r}
svytable(~alfonso_cohort + live_chernobyl, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + live_chernobyl, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

## Parental Alcohol/Drug Use

```{r}
# mother alc/drug problem
svytable(~alfonso_cohort + ch52, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + ch52, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# father alc/drug problem
svytable(~alfonso_cohort + ch82, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + ch82, design = SuicidePart2) %>%
  addmargins() %>%
  round()
```

## Parental Suicidality

```{r}
# mother suicidality
svytable(~alfonso_cohort + ch67, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + ch67, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# father suicidality
svytable(~alfonso_cohort + ch97, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + ch97, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

## Abortions

```{r}
# had an abortion
svytable(~alfonso_cohort + cn6, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + cn6, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# number of abortions
### continuous variable so frequency table less intuitive; just wanted to know
svytable(~alfonso_cohort + cn6a, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + cn6a, design = SuicidePart2) %>%
  addmargins() %>%
  round()
```

## Social Network

```{r}
# ability to rely on friends/family
svytable(~alfonso_cohort + sn6, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + sn6, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# ability to open up
svytable(~alfonso_cohort + sn6, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + sn6, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# contact with family
svytable(~alfonso_cohort + sn1, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + sn1, design = SuicidePart2) %>%
  addmargins() %>%
  round()
```

```{r}
# contact with friends
svytable(~alfonso_cohort + sn2, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + sn2, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

## Mental Disorders

```{r}
# affective
svytable(~alfonso_cohort + aff, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + aff, design = SuicidePart2) %>% 
  addmargins() %>% 
  round()
```

```{r}
# alcohol
svytable(~alfonso_cohort + alc, design = SuicidePart2) %>% 
  addmargins() %>% 
  round()
svytable(~brom3_agecohort + alc, design = SuicidePart2) %>% 
  addmargins() %>% 
  round()
```

```{r}
# ied
svytable(~alfonso_cohort + ied, design = SuicidePart2) %>% 
  addmargins() %>% 
  round()
svytable(~brom3_agecohort + ied, design = SuicidePart2) %>% 
  addmargins() %>% 
  round()
```

```{r}
# anxiety
svytable(~alfonso_cohort + aff, design = SuicidePart2) %>% 
  addmargins() %>% 
  round()
svytable(~brom3_agecohort + aff, design = SuicidePart2) %>%
  addmargins() %>% 
  round()
```

```{r}
# any
svytable(~alfonso_cohort + any, design = SuicidePart2) %>% 
  addmargins() %>% 
  round()
svytable(~brom3_agecohort + any, design = SuicidePart2) %>% 
  addmargins() %>% 
  round()
```

## Suicidality

```{r}
# ideate
svytable(~alfonso_cohort + ideate, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + ideate, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# plan
svytable(~alfonso_cohort + plan, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + plan, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# attempt
svytable(~alfonso_cohort + attempt, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + attempt, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# attempt without planning
attemptnoplan <-
  cididata_pt2 %>%
  filter(attempt == 1 & plan == 0)
svyattemptnoplan <-
  svydesign(ids = ~secu, strata = ~strata, weights = ~weight2, nest = T, 
            data = subset(attemptnoplan, attemptnoplan$weight2>0))
options(survey.lonely.psu = "adjust")
svytable(~alfonso_cohort, design = svyattemptnoplan) %>% round()
svytable(~brom3_agecohort, design = svyattemptnoplan) %>% round()
```

```{r}
# ideate without planning or attempting
ideate_only <-
  cididata_pt2 %>%
  filter(ideate == 1 & plan == 0 & attempt == 0)
svyideate <-
  svydesign(ids = ~secu, strata = ~strata, weights = ~weight2, nest = T, 
            data = subset(ideate_only, ideate_only$weight2>0))
options(survey.lonely.psu = "adjust")
svytable(~brom3_agecohort, design = svyideate)  %>% 
  addmargins() %>%
  round()
```

```{r}
# ideate, plan, and attempt by cohort
all3 <-
  cididata_pt2 %>%
  filter(ideate == 1 & plan == 1 & attempt == 1)
svyall3 <-
  svydesign(ids = ~secu, strata = ~strata, weights = ~weight2, nest = T, 
            data = subset(all3, all3$weight2>0))
options(survey.lonely.psu = "adjust")
svytable(~alfonso_cohort, design = svyall3) %>% round()
svytable(~brom3_agecohort, design = svyall3) %>% round()
```

## Religion

### Practiced Religion

```{r}
# orthodox counts by cohort
svytable(~alfonso_cohort + de32_1, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
svytable(~brom3_agecohort + de32_1, design = SuicidePart2) %>% 
  addmargins() %>%
  round()
```

```{r}
# uniate counts by cohort
svytable(~alfonso_cohort + de32_2, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + de32_2, design = SuicidePart2) %>%
  addmargins() %>%
  round()
```

```{r}
# other religion counts by cohort
svytable(~alfonso_cohort + de32_other, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + de32_other, design = SuicidePart2) %>%
  addmargins() %>%
  round()
```

```{r}
# no religion counts by cohort
svytable(~alfonso_cohort + de32_9, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + de32_9, design = SuicidePart2) %>%
  addmargins() %>%
  round()
```

### Religiosity

```{r}
# religiosity counts
svytable(~alfonso_cohort + de34, design = SuicidePart2) %>%
  addmargins() %>%
  round()
svytable(~brom3_agecohort + de34, design = SuicidePart2) %>%
  addmargins() %>%
  round()
```

# Univariate Models

## Cohort

```{r}
# Bromet cohort
svyglm(ideate~brom3_agecohort, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~brom3_agecohort, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~brom3_agecohort, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# Alfonso cohort
svyglm(ideate~alfonso_cohort, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~alfonso_cohort, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~alfonso_cohort, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Sex

```{r}
svyglm(ideate~SEX, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~SEX, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~SEX, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Religion

```{r}
# Orthodox
svyglm(ideate~de32_1, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~de32_1, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~de32_1, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# Uniate
svyglm(ideate~de32_2, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~de32_2, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~de32_2, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# Other
svyglm(ideate~de32_other, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~de32_other, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~de32_other, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# None
svyglm(ideate~de32_9, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~de32_9, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~de32_9, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# importance of religion
svyglm(ideate~de34, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~de34, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~de34, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Marital Status

```{r}
svyglm(ideate~marital_status, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~marital_status, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~marital_status, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Chronic Conditions

```{r}
# any chronic condition  
svyglm(ideate~any_cc, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~any_cc, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~any_cc, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Socio-economic Status

```{r}
# Years of Education
svyglm(ideate~de20, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~de20, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~de20, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# monthly HH income
svyglm(ideate~fnu1, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~fnu1, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~fnu1, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# financial status
svyglm(ideate~financial_status, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~financial_status, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~financial_status, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# employment status
svyglm(ideate~emp, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~emp, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~emp, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Urbanicity

```{r}
svyglm(ideate~io16, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~io16, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~io16, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Proximity to Chernobyl

```{r}
svyglm(ideate~live_chernobyl, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~live_chernobyl, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~live_chernobyl, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Parental Substance Use

```{r}
# mother
svyglm(ideate~ch52, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~ch52, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~ch52, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# father
svyglm(ideate~ch82, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~ch82, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~ch82, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Parental Suicidality

```{r}
# mother
svyglm(ideate~ch67, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~ch67, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~ch67, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# father
svyglm(ideate~ch97, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~ch97, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~ch97, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Abortions

```{r}
# have you ever had an abortion?
svyglm(ideate~cn6, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~cn6, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~cn6, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# number of abortions
svyglm(ideate~cn6a, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~cn6a, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~cn6a, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Social Network

```{r}
# social network interaction
svyglm(ideate~sn_scale, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~sn_scale, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~sn_scale, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# reliance
svyglm(ideate~SN6, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~SN6, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~SN6, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# ability to open up
svyglm(ideate~SN7, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~SN7, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~SN7, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

## Mental Disorders

```{r}
# anxiety
svyglm(ideate~anx, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~anx, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~anx, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# affective
svyglm(ideate~aff, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~aff, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~aff, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# alc
svyglm(ideate~alc, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~alc, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~alc, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# ied
svyglm(ideate~ied, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~ied, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~ied, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

```{r}
# any
svyglm(ideate~any, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(plan~any, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
svyglm(attempt~any, family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```



# Multi-variate Models

## Demographics

Full Demographics
```{r}
# ideate
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+de32_1+de32_2+
         de32_other+de32_9+emp+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
# plan
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+de32_1+de32_2+
         de32_other+de32_9+emp+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
# attempt
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+de32_1+de32_2+
         de32_other+de32_9+emp+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

Eliminate Employment
```{r}
# ideate
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+de32_1+de32_2+
         de32_other+de32_9+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
# plan
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+de32_1+de32_2+
         de32_other+de32_9+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
# attempt
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+de32_1+de32_2+
         de32_other+de32_9+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

Eliminate Religion
```{r}
# ideate
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
# plan
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
# attempt
svyglm(ideate~brom3_agecohort+SEX+io16+de20+financial_status+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```

Eliminate Financial Status
```{r}
# ideate
svyglm(ideate~brom3_agecohort+SEX+io16+de20+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
# plan
svyglm(ideate~brom3_agecohort+SEX+io16+de20+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
# attempt
svyglm(ideate~brom3_agecohort+SEX+io16+de20+married,
         family = quasibinomial("logit"), design = SuicidePart2) %>%
  summary()
```





